Network Deliberation: The role of network structure in large-scale, internet-enabled, participatory decision-making

### 2022-07-08 UMich/chapters/ch03-NetDelibABM.tex
Import NetDelibExp and formatting fixes.
Update ch3 based on feedback and additional results.

Communication in large collaborations is necessarily restricted when group size exceeds individual members' capacity for communication. The structure of the resulting communication network is an important factor in the success of collaborative tasks \cite{kearns_experiments_2012, mason_collaborative_2012, mason_propagation_2008}, such as deliberation. Among successful mass deliberative projects, communication networks often exhibits a common structure: small interlocking groups \cite{benkler_coases_2002, gonzalez-bailon_networked_2016, brugh_combining_2019, laloux_reinventing_2014}. A similar structure has been observed in the interlocking directorates of corporate boards \cite{karau_social_1993} and the interlocking publics of the public sphere \cite{habermas_structural_1991}, as well as utilized for collective design in network rotation \cite{salehi_hive_2018}.
These interlocking groups have been given various names: committees, working groups, projects, modules, affinity groups, circles, teams, cores, nodes, zones, cells, or syndicates.
We shall use the term {\em pods} to encompass all groups exhibiting two key characteristics: small enough to enable deliberation, and interlocking to enable information diffusion.
We shall use the term {\em network deliberation} to refer to mass deliberation using an interlocking pod structure.
Communication network structure also influences the success of collaborations by controlling the speed of information diffusion \cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,barkoczi_social_2016, gomez_clustering_2019,derex_partial_2016,kearns_experiments_2012}. Structurally efficient networks enable fast diffusion and favor exploitation of known information over exploration of the unknown \cite{lazer_network_2007, barkoczi_social_2016}. In the context of network deliberation, structural efficiency is determined by how individuals are assigned to pods.
We will focus on two such methods: one efficient, one inefficient.

@@

We model network deliberation using a social learning framework to address two questions. How effective is network deliberation compared to conventional single-group deliberation? And how do network efficiency and individual behavior influence the outcome of network deliberation? We present the following three contributions.
First, network deliberation out-performs conventional deliberation in both solution speed and quality when agents rely heavily on social learning. This suggests that network deliberation is a promising deliberation design for groups with a high degree of social influence. Second, network deliberation performs best on structurally efficient networks when agents exhibit conformist behavior, while it performs best on structurally inefficient networks when agents greedily maximize solution quality, consistent with findings for conventional networks \cite{barkoczi_social_2016}.
Third, the naive greedy strategy can be modified to improve performance on conventional networks despite using strictly less information. In the case of network deliberation, the naive and modified greedy strategies are equivalent.

@@

To model network deliberation, we construct interlocking networks in stages. At each stage, agents are partitioned into small {\em pods} and connected to all other agents in the same pod.
Our choice of pod size is informed by real-world The upper limit of effective small group size has been estimated variously as five \cite{freeman_tyranny_1972}, five--eight\cite{lohman_designing_2000}, and eight \cite{miflin_small_2004}.
We choose a pod size of 5.
Different methods for assigning agents to pods produce networks with different properties.
Interlocking structure is created when agents are placed with others they have not yet interacted with.
We thus require that pod assignment methods satisfy the following mixing property:
\begin{property}
\label{prop:mixing}
For any agent $v$, and any two assignment stages $t$, $t^\prime$, the probability that at least one neighbor of $v$ at stage $t$ is also a neighbor at stage $t^\prime$ approaches 0 as $|V|$ grows.
\end{property}
We study two such methods: a random assignment method that produces structurally efficient networks, and a long-path method that produces inefficient networks. For comparison, we also simulate conventional deliberation. While the potential communication links in conventional deliberation form a fully connected network, actual communication is better modeled by preferential attachment \cite{barabasi_emergence_1999} or small-world \cite{watts_collective_1998} networks (see Methods).

@@

The simulation begins at time $t=0$ by generating a set of initial solutions $s_{v,0}$ for the agents.
These are generated randomly, with each possible solution having equal probability.
The simulation proceeds iteratively.
At time $t$ each agent applies one of several {\em learning strategies}, to determine its preferred solution at time $t+1$.
Learning strategies can rely on the agent's own solution, the solutions of its neighbors, and potentially additional information shared by its neighbors.
Learning strategies may also incorporate information about the objective function, modeling an agents' ability to evaluate the quality of solutions.
To allow for ties, learning strategies produce a set of solutions rather than a single solution.
In our simulations, we choose winners at random in the case of a tie.
We present results for 1000 randomly generated NK model objectives.
with each network/strategy combination simulated once per objective function.
In keeping with other authors \cite{barkoczi_social_2016, lazer_network_2007} we use $N=15$ and $K=6$.
We allow each simulation to proceed for 300 iterations, which we have found sufficient to guarantee convergence with our chosen parameters.

@@

\subsection{Learning Strategies}
The choice of network structure defines which agents can exchange information, but not how those agents act on the information received. An agent's actions based on available information are determined by that agent's {\em learning strategy}. Learning strategies can be divided into {\em individual learning strategies} which use only information directly observable by the agent, and {\em social learning strategies} which use information communicated by neighboring agents.
Generally, a learning strategy may incorporate both social and individual components.
In this paper, we consider three separate strategies: {\em best-neighbor}, {\em confident-neighbor}, and {\em conform}.
Each is combined with the same mutation-based individual learning strategy.

To understand why real-world deliberators might choose different strategies,
it is necessary to realize that the social learning strategies available to an
individual depend on that individual's ability to evaluate the quality of candidate solutions.
Individuals with less information about solution quality, must rely
more heavily on the recommendations and influence of their peers.
We formalize an agent's ability to evaluate the quality of a candidate solution
as its {\em capabilities}, which we now explore in further detail.

\subsubsection{Agent Capabilities}
\label{sec:capability}
In human social learning, the ability of individuals to evaluate the quality of a solution can vary with factors such as expertise and task type. When comparing learning strategies, it will be helpful to classify them according to the capabilities they require of agents. We formalize these capabilities as oracle functions, which accept one or more task solutions as input and reveal whether the supplied state(s) satisfy some particular property.

@@

Confident-neighbor differs from best-neighbor because of two subtle but important considerations. First, an agent's neighbors need not be adjacent to each other. Second, an agent's neighbors can be adjacent to others outside that agent's neighborhood. As a result, an agent might receive zero, one, or many broadcasts. The exception is when agents belong to a clique (e.g., in network deliberation), in which case agents receive exactly one broadcast for each maximal solution in the clique, thus yielding the same results as best-neighbor. Confident-neighbor is thus more appropriate than best-neighbor for comparing network deliberation to single group deliberation, as the same information is utilized in both cases.

@@

Here we present the results of 1000 runs of an agent-based model of deliberation.
In each run, an NK model is generated (N=15, K=6) and the model is simulated for 300
iterations for each network/strategy combination.
The results of these simulations are shown in Figure \ref{fig:results}.
Figures \ref{fig:results-frac-parallel} and \ref{fig:results-frac-fallback} show pairwise comparisons of solution quality between strategy/network settings. Figures \ref{fig:results-bn-parallel-dist}--\ref{fig:results-conf-fallback-dist} show the complete solution quality distributions for all settings.
Tables \ref{tab:t-instrat-fallback}--\ref{tab:t-innet-parallel} show the t-values and Bonferroni-corrected p-values for comparisons across networks and strategies.

@@

\begin{figure*}[]
    \label{fig:results}
    \centering
    \begin{minipage}{3.33in}
        \centering
        \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-perf-both.eps}
    \end{minipage}%
    \begin{minipage}{1.875in}
    \centering
    \includegraphics[width=1.875in]{chapters/figures/NetDelibABM/fig-converge-both.eps}
    \end{minipage}
\caption{
Solution quality and convergence time for agent-based simulations of different learning strategies. Error bars represent 95\% confidence interval. Results for network deliberation are shown shaded.
}
\end{figure*}

\begin{figure}
    \label{fig:results-frac-parallel}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-result-frac-parallel.eps}
\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for parallel individual learning. In the case of a tie, weight is divided evenly.}
\end{figure}

\begin{figure}
    \label{fig:results-frac-fallback}
    \centering
%    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-result-frac-parallel.eps}
\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for fallback individual learning. In the case of a tie, weight is divided evenly.}
\end{figure}

\begin{figure}
    \label{fig:results-bn-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-bn-parallel-dist.eps}
\caption{Solution quality distribution for best-neighbor strategy with parallel individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-cn-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-cn-parallel-dist.eps}
\caption{Solution quality distribution for confident-neighbor strategy with parallel individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-conf-parallel-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-conf-parallel-dist.eps}
\caption{Solution quality distribution for the conform strategy with parallel individual learning.}
\end{figure}

\begin{figure}
    \label{fig:results-bn-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-bn-fallback-dist.eps}
\caption{Solution quality distribution for best-neighbor strategy with fallback individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-cn-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-cn-fallback-dist.eps}
\caption{Solution quality distribution for confident-neighbor strategy with fallback individual learning.}
\end{figure}
\begin{figure}
    \label{fig:results-conf-fallback-dist}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-conf-fallback-dist.eps}
\caption{Solution quality distribution for the conform strategy with fallback individual learning.}
\end{figure}

\begin{table*}[]
    \label{tab:t-instrat-fallback}
    \centering
    \begin{tabular}{l|ll|ccc}
        Strategy & Net A & Net B & $\overline{B - A}$ & t & p* \\
        \hline
Best Neighbor&Pref. Attach.&Small World&-8.70e-02&-1.33e+01&1.27e-35\\
Best Neighbor&Pref. Attach.&Long Path&-5.98e-02&-8.62e+00&1.51e-15\\
Best Neighbor&Pref. Attach.&Random Pod&-1.15e-02&-1.83e+00&4.01e+00\\
Best Neighbor&Small World&Pref. Attach.&8.70e-02&1.33e+01&1.27e-35\\
Best Neighbor&Small World&Long Path&2.72e-02&4.53e+00&3.88e-04\\
Best Neighbor&Small World&Random Pod&7.55e-02&1.18e+01&1.66e-28\\
Best Neighbor&Long Path&Pref. Attach.&5.98e-02&8.62e+00&1.51e-15\\
Best Neighbor&Long Path&Small World&-2.72e-02&-4.53e+00&3.88e-04\\
Best Neighbor&Long Path&Random Pod&4.83e-02&7.34e+00&2.69e-11\\
Best Neighbor&Random Pod&Pref. Attach.&1.15e-02&1.83e+00&4.01e+00\\
Best Neighbor&Random Pod&Small World&-7.55e-02&-1.18e+01&1.66e-28\\
Best Neighbor&Random Pod&Long Path&-4.83e-02&-7.34e+00&2.69e-11\\
\hline
Confident Neighbor&Pref. Attach.&Small World&-7.52e-02&-1.13e+01&2.94e-26\\
Confident Neighbor&Pref. Attach.&Long Path&2.39e-03&3.64e-01&4.30e+01\\
Confident Neighbor&Pref. Attach.&Random Pod&5.80e-02&8.88e+00&1.86e-16\\
Confident Neighbor&Small World&Pref. Attach.&7.52e-02&1.13e+01&2.94e-26\\
Confident Neighbor&Small World&Long Path&7.76e-02&1.21e+01&1.08e-29\\
Confident Neighbor&Small World&Random Pod&1.33e-01&1.92e+01&1.36e-68\\
Confident Neighbor&Long Path&Pref. Attach.&-2.39e-03&-3.64e-01&4.30e+01\\
Confident Neighbor&Long Path&Small World&-7.76e-02&-1.21e+01&1.08e-29\\
Confident Neighbor&Long Path&Random Pod&5.56e-02&8.50e+00&4.00e-15\\
Confident Neighbor&Random Pod&Pref. Attach.&-5.80e-02&-8.88e+00&1.86e-16\\
Confident Neighbor&Random Pod&Small World&-1.33e-01&-1.92e+01&1.36e-68\\
Confident Neighbor&Random Pod&Long Path&-5.56e-02&-8.50e+00&4.00e-15\\
\hline
Conform&Pref. Attach.&Small World&3.60e-02&6.78e+00&1.24e-09\\
Conform&Pref. Attach.&Long Path&-1.63e-01&-2.22e+01&2.25e-87\\
Conform&Pref. Attach.&Random Pod&-2.28e-01&-3.19e+01&9.08e-153\\
Conform&Small World&Pref. Attach.&-3.60e-02&-6.78e+00&1.24e-09\\
Conform&Small World&Long Path&-1.99e-01&-3.17e+01&1.59e-151\\
Conform&Small World&Random Pod&-2.64e-01&-4.43e+01&2.20e-236\\
Conform&Long Path&Pref. Attach.&1.63e-01&2.22e+01&2.25e-87\\
Conform&Long Path&Small World&1.99e-01&3.17e+01&1.59e-151\\
Conform&Long Path&Random Pod&-6.48e-02&-8.31e+00&1.79e-14\\
Conform&Random Pod&Pref. Attach.&2.28e-01&3.19e+01&9.08e-153\\
Conform&Random Pod&Small World&2.64e-01&4.43e+01&2.20e-236\\
Conform&Random Pod&Long Path&6.48e-02&8.31e+00&1.79e-14\\
\hline
    \end{tabular}
    \caption{Two-tailed paired t-values across networks, within strategies. Results are for fallback individual learning. For all rows, dof=999 and $p^*$ is the Bonferroni-corrected p-value with m=60.}
\end{table*}

\begin{table*}[]
    \label{tab:t-innet-fallback}
    \centering
    \begin{tabular}{l|ll|ccc}
        Network & Strategy A & Strategy B & $\overline{B - A}$ & t & p* \\
        \hline
Pref. Attach.&Best Neighbor&Confident Neighbor&-6.43e-02&-9.39e+00&2.33e-18\\
Pref. Attach.&Best Neighbor&Conform&8.96e-02&1.19e+01&6.83e-29\\
Pref. Attach.&Confident Neighbor&Best Neighbor&6.43e-02&9.39e+00&2.33e-18\\
Pref. Attach.&Confident Neighbor&Conform&1.54e-01&2.06e+01&7.57e-77\\
Pref. Attach.&Conform&Best Neighbor&-8.96e-02&-1.19e+01&6.83e-29\\
Pref. Attach.&Conform&Confident Neighbor&-1.54e-01&-2.06e+01&7.57e-77\\
\hline
Small World&Best Neighbor&Confident Neighbor&-5.26e-02&-8.39e+00&9.70e-15\\
Small World&Best Neighbor&Conform&2.13e-01&3.52e+01&4.46e-175\\
Small World&Confident Neighbor&Best Neighbor&5.26e-02&8.39e+00&9.70e-15\\
Small World&Confident Neighbor&Conform&2.65e-01&4.45e+01&1.24e-237\\
Small World&Conform&Best Neighbor&-2.13e-01&-3.52e+01&4.46e-175\\
Small World&Conform&Confident Neighbor&-2.65e-01&-4.45e+01&1.24e-237\\
\hline
Long Path&Best Neighbor&Confident Neighbor&-2.12e-03&-3.42e-01&4.39e+01\\
Long Path&Best Neighbor&Conform&-1.37e-02&-1.71e+00&5.20e+00\\
Long Path&Confident Neighbor&Best Neighbor&2.12e-03&3.42e-01&4.39e+01\\
Long Path&Confident Neighbor&Conform&-1.16e-02&-1.44e+00&8.96e+00\\
Long Path&Conform&Best Neighbor&1.37e-02&1.71e+00&5.20e+00\\
Long Path&Conform&Confident Neighbor&1.16e-02&1.44e+00&8.96e+00\\
\hline
Random Pod&Best Neighbor&Confident Neighbor&5.18e-03&8.40e-01&2.41e+01\\
Random Pod&Best Neighbor&Conform&-1.27e-01&-1.64e+01&1.07e-51\\
Random Pod&Confident Neighbor&Best Neighbor&-5.18e-03&-8.40e-01&2.41e+01\\
Random Pod&Confident Neighbor&Conform&-1.32e-01&-1.67e+01&1.39e-53\\
Random Pod&Conform&Best Neighbor&1.27e-01&1.64e+01&1.07e-51\\
Random Pod&Conform&Confident Neighbor&1.32e-01&1.67e+01&1.39e-53\\
\hline
    \end{tabular}
    \caption{Two-tailed paired t-values across strategies, within networks. Results are for fallback individual learning. For all rows, dof=999 and $p^*$ is the Bonferroni-corrected p-value with m=60.}
\end{table*}

>>>>

Communication in large collaborations is necessarily restricted when group size exceeds individual members' capacity for communication. The structure of the resulting communication network is an important factor in the success of collaborative tasks \cite{kearns_experiments_2012, mason_collaborative_2012, mason_propagation_2008}, such as deliberation. Among successful mass deliberative projects, communication networks often exhibits a common structure: small interlocking groups \cite{benkler_coases_2002, gonzalez-bailon_networked_2016, brugh_combining_2019, laloux_reinventing_2014}. A similar structure has been observed in the interlocking directorates of corporate boards \cite{karau_social_1993} and the interlocking publics of the public sphere \cite{habermas_structural_1991}, as well as utilized for collective design in network rotation \cite{salehi_hive_2018}.
These interlocking groups have been given various names: committees, working groups, projects, modules, affinity groups, circles, teams, cores, nodes, zones, cells, or syndicates.
We shall use the term {\em pods} to encompass all groups exhibiting two key characteristics: small enough to enable deliberation, and interlocking to enable information diffusion.
We shall use the term {\em network deliberation} to refer to mass deliberation using an interlocking pod structure.
Communication network structure also influences the success of collaborations by limiting the maximum speed of information diffusion \cite{lazer_network_2007,mason_propagation_2008,mason_collaborative_2012,barkoczi_social_2016, gomez_clustering_2019,derex_partial_2016,kearns_experiments_2012}.
Structurally efficient networks,
those with typically short paths between individuals,
enable fast diffusion and favor exploitation of known information over exploration of the unknown \cite{lazer_network_2007, barkoczi_social_2016}. In the context of network deliberation, structural efficiency is determined by how individuals are assigned to pods.
We will focus on two such methods: one efficient, one inefficient.

@@

We apply a formal social learning framework to model network deliberation.
Specifically, we address two questions. How effective is network deliberation compared to conventional single-group deliberation? And how do network efficiency and individual behavior influence the outcome of network deliberation?
We present the following three contributions.
First, network deliberation out-performs conventional deliberation in both solution speed and quality when agents rely heavily on social learning. This suggests that network deliberation is a promising deliberation design for groups with a high degree of social influence. Second, network deliberation performs best on structurally efficient networks when agents exhibit conformist behavior, while it performs best on structurally inefficient networks when agents greedily maximize solution quality, consistent with findings for conventional networks \cite{barkoczi_social_2016}.
Third, the naive greedy strategy can be modified to improve performance on conventional networks despite using strictly less information. In the case of network deliberation, the naive and modified greedy strategies are equivalent.

@@

To model network deliberation, we construct interlocking networks in stages. At each stage, agents are partitioned into small {\em pods} and connected to all other agents in the same pod.
Our choice of pod size is informed by studies of real-world group dynamics.
The upper limit of effective small group size has been estimated variously as five \cite{freeman_tyranny_1972}, five--eight\cite{lohman_designing_2000}, and eight \cite{miflin_small_2004}.
We choose a pod size of 5.
Different methods for assigning agents to pods produce networks with different properties.
Interlocking structure is created when agents are placed with others they have not yet interacted with.
We thus require that pod assignment methods satisfy the following mixing property:
\begin{property}
\label{prop:mixing}
For any agent $v$, and any two assignment stages $t$, $t^\prime$, the probability that at least one neighbor of $v$ at stage $t$ is also a neighbor at stage $t^\prime$ approaches 0 as $|V|$ grows.
\end{property}
We study two such methods: a random assignment method that produces structurally efficient networks, and a long-path method that produces inefficient networks. For comparison, we also simulate conventional deliberation. While the potential communication links in conventional deliberation form a fully connected network, actual communication is better modeled by preferential attachment \cite{barabasi_emergence_1999} or small-world \cite{watts_collective_1998} networks (see Methods).

@@

The simulation begins at time $t=0$ by generating a set of initial solutions $s_{v,0}$ for the agents.
These are generated randomly, with each possible solution having equal probability.
The simulation proceeds iteratively.
At time $t$ each agent applies one of several {\em learning strategies}, to determine its preferred solution at time $t+1$.
Learning strategies can rely on the agent's own solution, the solutions of its neighbors, and potentially additional information shared by its neighbors.
Learning strategies may also incorporate information about the objective function, modeling an agents' ability to evaluate the quality of solutions.
To allow for ties, learning strategies produce a set of solutions rather than a single solution.
In our simulations, we choose winners at random in the case of a tie.
We present results for 1000 randomly generated NK model objectives.
with each network/strategy combination simulated once per objective function.
In keeping with other authors \cite{barkoczi_social_2016, lazer_network_2007} we use $N=15$ and $K=6$.
We allow each simulation to proceed for 300 iterations, which we have found sufficient to guarantee convergence with our chosen parameters.
For real-world comparison, on average, an active English-language Wikipedia editor makes about 45 edits per month \cite{noauthor_wikipediastatistics_2022}.

@@

\subsection{Learning Strategies}
The choice of network structure defines which agents can exchange information, but not how those agents act on the information received. An agent's actions based on available information are determined by that agent's {\em learning strategy}. Learning strategies can be divided into {\em individual learning strategies} which use only information directly observable by the agent, and {\em social learning strategies} which use information communicated by neighboring agents.
Generally, a learning strategy may incorporate both social and individual components.
In this paper, we consider three separate strategies: {\em best-neighbor}, {\em confident-neighbor}, and {\em conform}.
Each is combined with the same individual learning strategy.

The social learning strategies available to an
individual depend on that individual's ability to evaluate the quality of candidate solutions.
Individuals with less information about solution quality, must rely
more heavily on the recommendations and influence of their peers.
We now develop a formalism describing an agent's ability to evaluate the quality of a candidate solution.
This formalism provides precise language for distinguishing between behavioral and informational constraints on agent behavior.

\subsubsection{Agent Capabilities}
\label{sec:capability}
In human social learning, the ability of individuals to evaluate the quality of a solution can vary with factors such as expertise and task type. When comparing learning strategies, it will be helpful to classify them according to the capabilities they require of agents. We formalize these {\em capabilities} as oracle functions, which accept one or more task solutions as input and reveal whether the states satisfy some particular property.

@@

Confident-neighbor can produce a different candidate than best-neighbor as a result of two subtle but important considerations.
First, an agent's neighbors need not be adjacent to each other. Second, an agent's neighbors can be adjacent to others outside that agent's neighborhood. As a result, an agent might receive zero, one, or many broadcasts.
The exception is when agents belong to a clique (e.g., in network deliberation), in which case agents receive exactly one broadcast for each maximal solution in the clique, thus yielding the same results as best-neighbor.
This equivalence is notable because confident-neighbor requires only single-state
comparisons rather than the arbitrary state comparisons used by best-neighbor.
Best-neighbor thus requires stronger capabilities to achieve the same results under conventional deliberation,
while confident-neighbor requires the same set of capabilities under both conventional and network deliberation.

@@

Here we present the results of 1000 runs of an agent-based model of deliberation.
In each run, an NK model is generated (N=15, K=6) and the model is simulated for 300
iterations for each network/strategy combination.
The results of these simulations are shown in Figure \ref{fig:ch03results}.
Figures \ref{fig:results-frac-parallel} and \ref{fig:results-frac-fallback} show pairwise comparisons of solution quality between strategy/network settings. Figures \ref{fig:results-bn-parallel-dist}--\ref{fig:results-conf-fallback-dist} show the complete solution quality distributions for all settings.
Tables \ref{tab:t-instrat-fallback}--\ref{tab:t-innet-parallel} show the t-values and Bonferroni-corrected p-values for comparisons across networks and strategies.

@@

\begin{figure*}[]
    \centering
    \begin{minipage}{3.33in}
        \centering
        \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-perf-both.eps}
    \end{minipage}%
    \begin{minipage}{1.875in}
    \centering
    \includegraphics[width=1.875in]{chapters/figures/NetDelibABM/fig-converge-both.eps}
    \end{minipage}
	\caption{
	Solution quality and convergence time for agent-based simulations of different learning strategies. Error bars represent 95\% confidence interval. Results for network deliberation are shown shaded.
	}
    \label{fig:ch03results}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-result-frac-parallel.eps}
	\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for parallel individual learning. In the case of a tie, weight is divided evenly.}
    \label{fig:results-frac-parallel}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/fig-result-frac-parallel.eps}
	\caption{Fraction of simulations in which the row condition outperforms the column condition. Results are shown for fallback individual learning. In the case of a tie, weight is divided evenly.}
    \label{fig:results-frac-fallback}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-bn-parallel-dist.eps}
	\caption{Solution quality distribution for best-neighbor strategy with parallel individual learning.}
\end{figure}
    \label{fig:results-bn-parallel-dist}

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-cn-parallel-dist.eps}
	\caption{Solution quality distribution for confident-neighbor strategy with parallel individual learning.}
    \label{fig:results-cn-parallel-dist}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-conf-parallel-dist.eps}
	\caption{Solution quality distribution for the conform strategy with parallel individual learning.}
    \label{fig:results-conf-parallel-dist}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-bn-fallback-dist.eps}
	\caption{Solution quality distribution for best-neighbor strategy with fallback individual learning.}
    \label{fig:results-bn-fallback-dist}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-cn-fallback-dist.eps}
	\caption{Solution quality distribution for confident-neighbor strategy with fallback individual learning.}
    \label{fig:results-cn-fallback-dist}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3.33in]{chapters/figures/NetDelibABM/results-conf-fallback-dist.eps}
	\caption{Solution quality distribution for the conform strategy with fallback individual learning.}
    \label{fig:results-conf-fallback-dist}
\end{figure}

\begin{table*}[]
    \centering
    \begin{tabular}{l|ll|ccc}
        Strategy & Net A & Net B & $\overline{B - A}$ & t & p* \\
        \hline
Best Neighbor&Pref. Attach.&Small World&-8.70e-02&-1.33e+01&1.27e-35\\
Best Neighbor&Pref. Attach.&Long Path&-5.98e-02&-8.62e+00&1.51e-15\\
Best Neighbor&Pref. Attach.&Random Pod&-1.15e-02&-1.83e+00&4.01e+00\\
Best Neighbor&Small World&Pref. Attach.&8.70e-02&1.33e+01&1.27e-35\\
Best Neighbor&Small World&Long Path&2.72e-02&4.53e+00&3.88e-04\\
Best Neighbor&Small World&Random Pod&7.55e-02&1.18e+01&1.66e-28\\
Best Neighbor&Long Path&Pref. Attach.&5.98e-02&8.62e+00&1.51e-15\\
Best Neighbor&Long Path&Small World&-2.72e-02&-4.53e+00&3.88e-04\\
Best Neighbor&Long Path&Random Pod&4.83e-02&7.34e+00&2.69e-11\\
Best Neighbor&Random Pod&Pref. Attach.&1.15e-02&1.83e+00&4.01e+00\\
Best Neighbor&Random Pod&Small World&-7.55e-02&-1.18e+01&1.66e-28\\
Best Neighbor&Random Pod&Long Path&-4.83e-02&-7.34e+00&2.69e-11\\
\hline
Confident Neighbor&Pref. Attach.&Small World&-7.52e-02&-1.13e+01&2.94e-26\\
Confident Neighbor&Pref. Attach.&Long Path&2.39e-03&3.64e-01&4.30e+01\\
Confident Neighbor&Pref. Attach.&Random Pod&5.80e-02&8.88e+00&1.86e-16\\
Confident Neighbor&Small World&Pref. Attach.&7.52e-02&1.13e+01&2.94e-26\\
Confident Neighbor&Small World&Long Path&7.76e-02&1.21e+01&1.08e-29\\
Confident Neighbor&Small World&Random Pod&1.33e-01&1.92e+01&1.36e-68\\
Confident Neighbor&Long Path&Pref. Attach.&-2.39e-03&-3.64e-01&4.30e+01\\
Confident Neighbor&Long Path&Small World&-7.76e-02&-1.21e+01&1.08e-29\\
Confident Neighbor&Long Path&Random Pod&5.56e-02&8.50e+00&4.00e-15\\
Confident Neighbor&Random Pod&Pref. Attach.&-5.80e-02&-8.88e+00&1.86e-16\\
Confident Neighbor&Random Pod&Small World&-1.33e-01&-1.92e+01&1.36e-68\\
Confident Neighbor&Random Pod&Long Path&-5.56e-02&-8.50e+00&4.00e-15\\
\hline
Conform&Pref. Attach.&Small World&3.60e-02&6.78e+00&1.24e-09\\
Conform&Pref. Attach.&Long Path&-1.63e-01&-2.22e+01&2.25e-87\\
Conform&Pref. Attach.&Random Pod&-2.28e-01&-3.19e+01&9.08e-153\\
Conform&Small World&Pref. Attach.&-3.60e-02&-6.78e+00&1.24e-09\\
Conform&Small World&Long Path&-1.99e-01&-3.17e+01&1.59e-151\\
Conform&Small World&Random Pod&-2.64e-01&-4.43e+01&2.20e-236\\
Conform&Long Path&Pref. Attach.&1.63e-01&2.22e+01&2.25e-87\\
Conform&Long Path&Small World&1.99e-01&3.17e+01&1.59e-151\\
Conform&Long Path&Random Pod&-6.48e-02&-8.31e+00&1.79e-14\\
Conform&Random Pod&Pref. Attach.&2.28e-01&3.19e+01&9.08e-153\\
Conform&Random Pod&Small World&2.64e-01&4.43e+01&2.20e-236\\
Conform&Random Pod&Long Path&6.48e-02&8.31e+00&1.79e-14\\
\hline
    \end{tabular}
    \caption{Two-tailed paired t-values across networks, within strategies. Results are for fallback individual learning. For all rows, dof=999 and $p^*$ is the Bonferroni-corrected p-value with m=60.}
    \label{tab:t-instrat-fallback}
\end{table*}

\begin{table*}[]
    \centering
    \begin{tabular}{l|ll|ccc}
        Network & Strategy A & Strategy B & $\overline{B - A}$ & t & p* \\
        \hline
Pref. Attach.&Best Neighbor&Confident Neighbor&-6.43e-02&-9.39e+00&2.33e-18\\
Pref. Attach.&Best Neighbor&Conform&8.96e-02&1.19e+01&6.83e-29\\
Pref. Attach.&Confident Neighbor&Best Neighbor&6.43e-02&9.39e+00&2.33e-18\\
Pref. Attach.&Confident Neighbor&Conform&1.54e-01&2.06e+01&7.57e-77\\
Pref. Attach.&Conform&Best Neighbor&-8.96e-02&-1.19e+01&6.83e-29\\
Pref. Attach.&Conform&Confident Neighbor&-1.54e-01&-2.06e+01&7.57e-77\\
\hline
Small World&Best Neighbor&Confident Neighbor&-5.26e-02&-8.39e+00&9.70e-15\\
Small World&Best Neighbor&Conform&2.13e-01&3.52e+01&4.46e-175\\
Small World&Confident Neighbor&Best Neighbor&5.26e-02&8.39e+00&9.70e-15\\
Small World&Confident Neighbor&Conform&2.65e-01&4.45e+01&1.24e-237\\
Small World&Conform&Best Neighbor&-2.13e-01&-3.52e+01&4.46e-175\\
Small World&Conform&Confident Neighbor&-2.65e-01&-4.45e+01&1.24e-237\\
\hline
Long Path&Best Neighbor&Confident Neighbor&-2.12e-03&-3.42e-01&4.39e+01\\
Long Path&Best Neighbor&Conform&-1.37e-02&-1.71e+00&5.20e+00\\
Long Path&Confident Neighbor&Best Neighbor&2.12e-03&3.42e-01&4.39e+01\\
Long Path&Confident Neighbor&Conform&-1.16e-02&-1.44e+00&8.96e+00\\
Long Path&Conform&Best Neighbor&1.37e-02&1.71e+00&5.20e+00\\
Long Path&Conform&Confident Neighbor&1.16e-02&1.44e+00&8.96e+00\\
\hline
Random Pod&Best Neighbor&Confident Neighbor&5.18e-03&8.40e-01&2.41e+01\\
Random Pod&Best Neighbor&Conform&-1.27e-01&-1.64e+01&1.07e-51\\
Random Pod&Confident Neighbor&Best Neighbor&-5.18e-03&-8.40e-01&2.41e+01\\
Random Pod&Confident Neighbor&Conform&-1.32e-01&-1.67e+01&1.39e-53\\
Random Pod&Conform&Best Neighbor&1.27e-01&1.64e+01&1.07e-51\\
Random Pod&Conform&Confident Neighbor&1.32e-01&1.67e+01&1.39e-53\\
\hline
    \end{tabular}
    \caption{Two-tailed paired t-values across strategies, within networks. Results are for fallback individual learning. For all rows, dof=999 and $p^*$ is the Bonferroni-corrected p-value with m=60.}
    \label{tab:t-innet-fallback}
\end{table*}
